\documentclass[a4paper]{article}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{url}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{verbatim} % for use of multi-line comments (using \begin{comment}...\end{comment}).
\usepackage[T1]{fontenc}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{xcolor}\hypersetup{colorlinks,linkcolor={red!50!black},citecolor={blue!50!black},urlcolor={blue!80!black}} % hyperref link color
\usepackage{cleveref}
\usepackage{multirow}
\newcommand\Tstrut{\rule{0pt}{2.6ex}}       % "top" strut
\newcommand\Bstrut{\rule[-0.9ex]{0pt}{0pt}} % "bottom" strut
\newcommand{\TBstrut}{\Tstrut\Bstrut} % top&bottom struts
\usepackage{longtable} % multiple page table
\crefname{figure}{figure}{figures}
\bibliographystyle{plain}




% altered page margins
\setlength{\parskip}{0.8em}
\addtolength{\topmargin}{-.5in}
\addtolength{\oddsidemargin}{-.5in}
\addtolength{\evensidemargin}{-.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\textheight}{0.7in}
\renewcommand{\arraystretch}{1.2} % table row

% source code listings
\definecolor{mygreen}{rgb}{0,0.6,0}
\definecolor{mygray}{rgb}{0.5,0.5,0.5}
\definecolor{mymauve}{rgb}{0.58,0,0.82}
\lstset{
  language=Java,
  backgroundcolor=\color{white},
  basicstyle=\footnotesize,
  breaklines=true,
  commentstyle=\color{mygreen},
  escapeinside={\%*}{*)},
  keywordstyle=\color{blue},
  stringstyle=\color{mymauve},
  frame=LB,
  numbers=left, numberstyle=\tiny
}

% requirements counter, taken from https://gist.github.com/atnon/5d19f288c9c1e2f1cdf5
\crefname{reqCounter}{requirement}{requirements}
\newcounter{reqCounter}\newcommand{\requirement}{\refstepcounter{reqCounter}Req. \arabic{reqCounter}}
% use case counter
\crefname{ucCounter}{use case}{use cases}
\newcounter{ucCounter}\newcommand{\usecase}{\refstepcounter{ucCounter}Use case \arabic{ucCounter}}



\title{GreenMirror: A Visualization and Animation Framework for State-Transition Models \\ {\large Bachelor assignment}}
\author{
	K.M. El Assal (s1097539) \\ 
	University of Twente \\ 
	P.O. Box 217, 7500AE Enschede, the Netherlands \\ 
	\texttt{k.m.elassal@student.utwente.nl} \\
	\\ 
	Exam committee: \\ 
	prof.dr.ir. A. Rensink \\ 
	dr. H.K. Hemmes \\
	\\
	repository: \url{https://github.com/iisys-/GreenMirror}
}
\date{\today}

\begin{document}

\maketitle
\begin{abstract}
State-transition models are often used to analyse the discrete dynamic behaviour of systems, although analysis may prove to be tedious when a system has a huge amount of possible states. A tool is being developed using the Java programming language and the JavaFX library to provide a different approach. Continuing previous work, this report describes the next step that has been made in the development of a framework that can visualize a system's states and animate transitions that result from a list of state-transitions. The user can define complex state-transition models during runtime which will be visualized according to the state-transitions the user also provides during runtime. The framework has been specifically designed to support future development by being modular, extensible and maintainable.
\end{abstract}

\newpage
\tableofcontents

\newpage
\input{introduction}
\newpage
\input{ferryman}
\newpage
\input{features}
\newpage
\input{design}
\newpage
\input{validation}
\newpage
\input{discussion}


\bibliography{bibliography}
\newpage
\appendix
\input{app_services}
\newpage
\input{app_seqdiagrams}

\end{document}